Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation

### 2011-02-22 Multiresolution_framework/ltx/manuscript.tex
added figures

\begin{algorithm}
\caption{Ensemble Kalman smoother}
\label{alg:EnKS}
% \begin{tabbing}
\begin{enumerate}
\item Initialise:
\begin{center}
 $\hat{\mathbf x}_0 $, $\mathbf P_0$  
\end{center}
\item
for $t\in\left\lbrace 0, \dots, T\right\rbrace $, calculate the state ensembles $\hat{\mathbf X}_t$ and the model errors ensemble $\mathbf W_t$ and propogate through the state equation:
\begin{equation*}
\hat{\mathbf X}_{i,t+1}^f=\mathbf A \hat{\mathbf X}_{i,t}^a+\mathbf W_{i,t}
\end{equation*}
calculate the predicted state and the predicted covariance matrix
\begin{equation*}
 \hat{\mathbf x}_{t+1}^f=\frac{1}{N}\sum_{i=1}^{N}\hat{\mathbf X}_{i,t+1}^f
\end{equation*}
\begin{equation*}
 \mathbf P_{t+1}^f=\frac{1}{N-1}\sum_{i=1}^{N}\left( \hat{\mathbf X}_{i,t+1}^f- \hat{\mathbf x}_{t+1}^f\right)\left( \hat{\mathbf X}_{i,t+1}^f- \hat{\mathbf x}_{t+1}^f\right)^\top
\end{equation*}
\item
compute $\mathbf X_4(t+1)$ and $\mathbf X_5(t+1)$ and the filtered state and the filtered covariance matrix:
\begin{equation*}
 \mathcal K_t=\mathbf C^{\top}(\mathbf C\mathbf{P}_{t+1}^f\mathbf C^{\top}+\boldsymbol\Sigma_v)^{-1}
\end{equation*}

\begin{equation*}
 \mathbf X_4(t+1)=\frac{1}{N-1}\sum_{i=1}^{N}(\hat{\mathbf X}_{i,t+1}^f-\hat{\mathbf x}^f_{t+1} )^\top\mathcal K_t (\mathbf Y_{i,t+1}-\mathbf C\hat{\mathbf{X}}_{i,t+1}^f)
\end{equation*}
\begin{equation*}
 \mathbf X_5(t+1)= \mathbf I +\mathbf X_4(t+1)
\end{equation*}
\begin{equation*}
 \hat{\mathbf X}_{t+1}^a=\hat{\mathbf X}_{t+1}^f \mathbf X_5(t+1)
\end{equation*}
\item compute the smooth ensemble for $t\in\left\lbrace 0, \dots, T\right\rbrace $
\begin{equation*}
 \hat{\mathbf{X}}_{t}^s=\hat{\mathbf X}_{t}^a \prod_{j=t+1}^{T}X_5(j)
\end{equation*}
\end{enumerate}
% \end{tabbing}
\end{algorithm}

@@

% \includegraphics[width=0.5\textwidth]{./Graph/aram1.eps}
% \caption{Multiresolution decomposition of a complex spatial mixing kernel (dark line) and the corresponding scaling and wavelet basis functions (light lines).}
% \label{fig:SpatialMixingKernel}
% \includegraphics[width=0.5\textwidth]{./Graph/aram2.eps}
% \caption{Spatial mixing kernel; estimated and true kernels are shown by solid and dashed line respectively; top panel is estimation with maximmum scale $j=0$ and bottom panel is estimation with maximum scale $j=1$. }
% \label{fig:SpatialMixingKernelEstimate}
% \begin{figure*}[!hb] 
% % \renewcommand*{\thesubfigure}{}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram35.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram310.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram350.eps}}\\ 
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3100.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3200.eps}} 
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3300.eps}}
% \caption{Spatial field at a number of time instants; estimated and true fields are shown by solid and dashed line respectively; the top panel of each plot is the estimate with maximmum scale $j=0$ and the bottom panel is the estimate with maximum scale $j=1$.}
% \label{fig:1DFieldEstimation}
% \end{figure*}
In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
 k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{0,l}\phi_{4;0,l}\left(s-r\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{4;j,l}\left(s-r\right)
\label{1DKernelDecompositionForSimulation}
 z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,0,l}\phi_{4;0,l}\left(s\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{4;j,l}\left(s\right)
\label{1DFieldDecompositionForSimulation}
Note that the number of translation operations depends on the spatial range of the data. It follows that the total number of terms in (\ref{1DKernelDecompositionForSimulation}) and (\ref{1DFieldDecompositionForSimulation}) are 8 and 47 respectively. The estimated kernel in \figurename{\ref{fig:SpatialMixingKernelEstimate} } is obtained for the cubic B-spline, with initial scale 0 and maximum scale 1. The EM algorithm is allowed to run for 30 iterations to avoid any issues regarding early stopping, though typically the change in $\parallel \mathbf{A} \parallel_{F}$ falls below $10^{-4} $ after less than 15 iterations. A total number of 500 estimation experiments are performed, where $v_t$ and $w_t$ are re-generated each trial.

@@

\subsection{Two dimensional example}
In order to demonstrate the ability of the developed model in higher dimensions, a two dimensional IDE model with a single B-spline kernel $\phi_{4;0,\mathbf{l}}\left(s_1-r_1,s_2-r_2\right) $ and $\mathbf l=[-2,-2]^ \top$ is used with parameter $\theta=1$. In this example spatial region $\mathcal{S}=[0,4]^2 $ is simulated over $t=\left\lbrace1 \cdots 200  \right\rbrace $ using $7$ scaling and wavelet functions at $j=0$ together with $24$ wavelet functions at $j=1$. Univariate cubic B-spline scaling and wavelet functions are used to generate 2-D basis functions using (\ref{eq:2Dscalingfunction}-\ref{eq:2Dwavelet_3}). A set of $250$ random  observation locations is used; $\mathbf{\Sigma}_v$ is taken the same as that in example 1 and $ \eta\left(s_1-r_1,s_2-r_2\right) =2.5\times\phi_{4,3,\mathbf{l}}\left(s_1-r_1,s_2-r_2\right)$ where $\mathbf l=[-2,-2]^ \top$. The histogram of the parameter estimates  in \figurename{\ref{fig:2DHist} is generated using 500 runs of the EM algorithm. For comparison, snapshots for the original and the corresponding coarse and fine field estimates at time instants 5, 50 and 150 are illustrated in \figurename{\ref{fig:2DFieldEstimation1}-\ref{fig:2DFieldEstimation3}}. In addition, the MISE of the dynamic field at some time instants are presented in Table \ref{table:ValidationResultField}.  This shows that the multiresolution IDE model can estimate the spatio-temporal dynamics of the original system accurately. The accuracy of the estimation remains consistent over time. Performance is improved significantly at $j=1$ compared to the case where $j=0$.
% \begin{figure}[!t] 
% \includegraphics[width=0.5\textwidth]{./Graph/aram5.eps}
% \caption{Distribution of the parameter estimate for 2-D Example over 500 runs of the EM algorithm. The dotted line indicates the true parameter.}
% \label{fig:2DHist}
% \begin{figure*}[!th] 
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6a.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6b.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram6c.eps}}\\ 
% \caption{Spatial field at t=5; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
% \label{fig:2DFieldEstimation1}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7a.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7b.eps}} 
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram7c.eps}}\\
% \caption{Spatial field at t=50; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
% \label{fig:2DFieldEstimation2}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8a.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8b.eps}} 
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram8c.eps}}
% \caption{Spatial field at t=150; a: True field; b: Estimated field with maximmum scale $j=0$; c: Estimated field with maximmum scale $j=1$.}
% \label{fig:2DFieldEstimation3}
% \end{figure*}

@@

By considering different levels of decomposition, the proposed approach could be used as a method of determining the appropriate scales of decomposition, within a model-selection framework. Combined with an approach to sparsely modelling spatial heterogeneity, such as boundary conditions, this would allow the application of this work to a real-world data set.
% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed
% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%
\newtheorem{lemma}{Lemma}
\begin{lemma}
Consider the zero-mean process $e_t\left(s\right)$ with covariance as defined by (\ref{eq:FieldCovariance}) then
 \mathbf{w}_t=\mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)e_t\left(\mathbf{s}\right)d\mathbf{s}
\label{eq:AppendixWt}
is a vector valued, zero mean normally distributed white noise process with covariance
\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{- \top}
and
 \boldsymbol\Pi=\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right)\eta\left(\mathbf s-\mathbf r\right)\boldsymbol\mu\left(\mathbf r\right)^\top d\mathbf{r}d\mathbf{s}
\label{lemma:FieldCovariance}
\end{lemma}
\begin{IEEEproof}
 Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf s)$ and hence $\mathbf{w}_t$ is also normally distributed. The expected value of $\mathbf w_t$ is given by 
 \mathbf E\left[ \mathbf w_t\right]&=& \mathbf{\Lambda}_{x}^{-1}\int_{\mathcal{S}}\boldsymbol\mu \left(\mathbf{s}\right)\mathbf E\left[e_t\left(\mathbf{s}\right)\right] d\mathbf{s} \nonumber \\
&=&0
and 
\mathbf \Sigma_w&{}={}&\mathbf E[ \mathbf w_t \mathbf w_{t}^{\top}]\nonumber\\
&=& \mathbf{\Lambda}_{x}^{-1}\mathbf E[\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right)e_t\left(\mathbf s\right)d\mathbf s\int_{\mathcal{S}}\boldsymbol\mu\left(\mathbf r\right)^{\top}e_t\left(\mathbf r\right)d\mathbf r]\mathbf{\Lambda}_{x}^{- \top} \nonumber \\
&=&\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right) \mathbf E[e_t\left(\mathbf s\right)e_t\left(\mathbf r\right)]\boldsymbol\mu\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Lambda}_{x}^{- \top} \nonumber\\
&=&{}\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\mathcal{S}}\boldsymbol\mu\left(\mathbf s\right) \eta\left(\mathbf s- \mathbf r \right)\boldsymbol\mu\left(\mathbf r\right)^{\top}d\mathbf r d\mathbf s\mathbf{\Lambda}_{x}^{- \top} \nonumber\\
&=&\mathbf{\Lambda}_{x}^{-1}\boldsymbol\Pi\mathbf{\Lambda}_{x}^{- \top}
\end{IEEEproof}
\begin{lemma}
Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively. Then the inner product of  $N_m\left(s-l_1\right)$  and $N_{m'}\left(s-l_2\right)$ can be calculated by 
\left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=&N_{m+m'}\left(m'+l_{2}-l_{1}\right) 
\label{lemma:InProduct}
\end{lemma}
\begin{IEEEproof}
The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $s=\frac{m}{2}$, i.e.
 N_{m}\left(\frac{m}{2}+s\right)=N_{m}\left(\frac{m}{2}-s\right)
\label{SymmetrySplieEq}
A direct consequence of (\ref{SymmetrySplieEq}) is 
 N_{m}\left(s\right)=N_{m}\left(m-s\right)
Therefore
\begin{IEEEeqnarray}{l}
\int_{-\infty}^{+\infty}N_{m}\left(s-l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m-s+l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
\qquad=\left(N_m \ast N_m'\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
\qquad=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
\qquad=N_{m+m'}\left(m'+l_{2}-l_{1}\right) \nonumber
\end{IEEEproof}
\section*{Reducing the computational complexity}\label{App:ReducedRTS}
The state-space representation of the spatio-temporal IDE \eqref{eq:StateEquation} and \eqref{eq:ObservationEquation} has a quadratic $\mathcal Q$-function in a form of \cite{Dewar2009}
\mathcal{Q}\left(\boldsymbol\theta,\boldsymbol\theta'\right)=2 \boldsymbol\theta^\top\boldsymbol\upsilon -\boldsymbol\theta^\top\boldsymbol\Upsilon\boldsymbol\theta
\label{eq:QFunction}
which has a maximum at
 \boldsymbol\theta=\boldsymbol\Upsilon^{-1}\boldsymbol\upsilon
where
\begin{equation}\label{eq:Upsilon}
 \boldsymbol\Upsilon=\sum_{i,j,k,m=1}^{n_x}\left[ \Xi_1\right] _{ij}\boldsymbol\gamma^{\left(k,j\right)}\left[\boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1} \boldsymbol\Lambda_{x}^{-1}\right]_{km} \boldsymbol\gamma^{\left(m,i\right)\mathsf{T}}
and
 \boldsymbol \upsilon=\sum_{i,j=1}^{n_x}\left[\Xi_0\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1} \right]_{ij}\boldsymbol\gamma^{\left(j,i\right)} 
where
 \boldsymbol\gamma^{(i,j)}=\int_{\mathcal S}\left[ \mu(s)\right]_i\left[ \mathbf M(s)\right] _{:j}ds
and $\left[ \mathbf M(s)\right] _{:j}$ denotes the $j$th column of $\mathbf M(s)$. The definitions of the $\Xi_0$ and $\Xi_1$ are the same as in \cite{Dewar2009}. Note that constant values with respect to $\boldsymbol \theta$ are ignored in \eqref{eq:QFunction}.
We define $n_x \times n_x$ block matrix $\mathbf U$ such that
\begin{equation}\label{eq:UMatrix}
 [\mathbf U]_{i,j}=\boldsymbol\gamma^{(i,j)\mathsf{T}}
substituting \eqref{eq:UMatrix} in \eqref{eq:Upsilon} we get
\begin{equation}\label{eq:UpsilonU}
 \boldsymbol\Upsilon=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\mathbf{U}^{\mathsf T} \boldsymbol\Lambda_{x}^{-1}\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf{U}]_{j,i}
and similarly substituting \eqref{eq:UMatrix} in \eqref{eq:Upsilon} we have
\begin{equation}\label{eq:upsilonU}
 \boldsymbol\upsilon=\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_0]_{i,j}[\Sigma_{w}^{-1}\boldsymbol\Lambda_{x}^{-1}\mathbf U]_{j,i}
with this substitution the second terms in \eqref{eq:UpsilonU} and \eqref{eq:upsilonU} can be pre-calculated and stored. This lowers the comutational complexity of the estimation algorithm and provides a dramatic increase in estimation speed.
\section*{Cross covariance matrix}\label{App:EnCrossCov}

>>>>

@@

\begin{figure}[!h] 
 \includegraphics[scale=1]{./Graph/ObservationFreqResponse.pdf}
 \caption{The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
 \label{fig:FreqResponse}
 \end{figure} 
\begin{figure}[!h] 
 \includegraphics[scale=1]{./Graph/Hist.pdf}
 \caption{Histograms of the parameter estimates over 100 realizations. In each of the subplots
the solid lines show the actual parameter values and the dotted lines show the means of the estimated
parameters. Left panel: The histogram of the central excitatory connectivity kernel basis function parameter
estimates, $\theta_0$. Right panel: The histogram of the surround inhibition connectivity kernel basis function parameter
estimates, $\theta_1$.}
 \label{fig:ParametersHistogram}
 \end{figure} 
\begin{figure}[!h] 
 %\includegraphics[width=0.5\textwidth]{./Graph/RMSE.pdf}
\includegraphics[scale=1]{./Graph/RMSE.pdf}
 \caption{RMSE of the estimated field at different spatial resolution.}
 \label{fig:RMSE}
 \end{figure} 
\begin{figure}[!h] 
 \includegraphics[scale=1]{./Graph/Field.pdf}
 \caption{Spatial field at one time instant for different spatial resolutions; estimated and true fields are
shown by dashed and solid lines respectively.}
 \label{fig:FreqResponse}
 \end{figure}

% \begin{figure}[!h] 
% \centering
% \includegraphics[width=0.5\textwidth]{./Graph/aram2.eps}
% \caption{Spatial mixing kernel; estimated and true kernels are shown by solid and dashed line respectively; top panel is estimation with maximmum scale $j=0$ and bottom panel is estimation with maximum scale $j=1$. }
% \label{fig:SpatialMixingKernelEstimate}
% \end{figure}
% \begin{figure*}[!hb] 
% % \renewcommand*{\thesubfigure}{}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram35.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram310.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram350.eps}}\\ 
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3100.eps}}
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3200.eps}} 
% \subfigure[][]{\includegraphics[width=2.18in]{./Graph/aram3300.eps}}
% \caption{Spatial field at a number of time instants; estimated and true fields are shown by solid and dashed line respectively; the top panel of each plot is the estimate with maximmum scale $j=0$ and the bottom panel is the estimate with maximum scale $j=1$.}
% \label{fig:1DFieldEstimation}
% \end{figure*}
In order to estimate the spatial mixing kernel and the spatio-temporal field, the  kernel and the field are decomposed using
\begin{equation}
 k\left(s-r\right)=\sum_{l \in \mathbb{Z}}\alpha_{0,l}\phi_{4;0,l}\left(s-r\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}}\beta_{j,l}\psi_{4;j,l}\left(s-r\right)
\label{1DKernelDecompositionForSimulation}
\end{equation}
\begin{equation}
 z_t\left(s\right)=\sum_{l \in \mathbb{Z}}x_{t,0,l}\phi_{4;0,l}\left(s\right)+\sum_{j=0}^{1} \sum_{l \in \mathbb{Z}} \check{x}_{t,j,l}\psi_{4;j,l}\left(s\right)
\label{1DFieldDecompositionForSimulation}
\end{equation}
Note that the number of translation operations depends on the spatial range of the data. It follows that the total number of terms in (\ref{1DKernelDecompositionForSimulation}) and (\ref{1DFieldDecompositionForSimulation}) are 8 and 47 respectively. The estimated kernel in \figurename{\ref{fig:SpatialMixingKernelEstimate} } is obtained for the cubic B-spline, with initial scale 0 and maximum scale 1. The EM algorithm is allowed to run for 30 iterations to avoid any issues regarding early stopping, though typically the change in $\parallel \mathbf{A} \parallel_{F}$ falls below $10^{-4} $ after less than 15 iterations. A total number of 500 estimation experiments are performed, where $v_t$ and $w_t$ are re-generated each trial.

@@

@@

By considering different levels of decomposition, the proposed approach could be used as a method of determining the appropriate scales of decomposition, within a model-selection framework. Combined with an approach to sparsely modelling spatial heterogeneity, such as boundary conditions, this would allow the application of this work to a real-world data set.
% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed
% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%
\newtheorem{lemma}{Lemma}
\begin{lemma}
Let $N_m\left(s-l_1\right)$ and $N_{m'}\left(s-l_2\right)$ be shifted B-spline functions of order $m$ and $m'$ respectively. Then the inner product of  $N_m\left(s-l_1\right)$  and $N_{m'}\left(s-l_2\right)$ can be calculated by 
\setlength{\arraycolsep}{0.0em}
\begin{eqnarray}
\left\langle N_{m}\left(s-l_{1}\right), N_{m'}\left(s-l_{2}\right)\right\rangle&=&N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=&N_{m+m'}\left(m'+l_{2}-l_{1}\right) 
\end{eqnarray}
\setlength{\arraycolsep}{5pt}
\label{lemma:InProduct}
\end{lemma}
\begin{IEEEproof}
The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $s=\frac{m}{2}$, i.e.
\begin{equation}
 N_{m}\left(\frac{m}{2}+s\right)=N_{m}\left(\frac{m}{2}-s\right)
\label{SymmetrySplieEq}
\end{equation}
A direct consequence of (\ref{SymmetrySplieEq}) is 
\begin{equation}
 N_{m}\left(s\right)=N_{m}\left(m-s\right)
\end{equation}
Therefore
\setlength{\arraycolsep}{0.0em}
\begin{IEEEeqnarray}{l}
\int_{-\infty}^{+\infty}N_{m}\left(s-l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m-s+l_{1}\right)N_{m'}\left(s-l_{2}\right)ds \nonumber \\
\qquad=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
\qquad=\left(N_m \ast N_m'\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
\qquad=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
\qquad=N_{m+m'}\left(m'+l_{2}-l_{1}\right) \nonumber
\end{IEEEeqnarray}
\setlength{\arraycolsep}{5pt}
\end{IEEEproof}
